Predicting information integration in pragmatic word learning across development

### 2020-11-19 papers/full_paper/models.Rmd
prag noise llh distribution kids

@@

```{r}
# webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.marginal.likelihood , sep='\n'),
#   packages ="webppl-csv",
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 1,
#   cores = 1
# )
# 
# read_csv("../../stats/data/llh_child_prag_param_free.csv")%>%
#   mutate(model = "pragmatic",
#          parameter = "parameter free")%>%
#   saveRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")

@@

>>>>

var steps = 5000
var samples = 1

@@

```{r}
webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.marginal.likelihood , sep='\n'),
  packages ="webppl-csv",
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 1,
  cores = 1
)

read_csv("../../stats/data/llh_child_prag_param_free.csv")%>%
  mutate(model = "pragmatic",
         parameter = "parameter free")%>%
  saveRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")

@@

var steps = 5000
var samples = 100
